### 2025-04-08 Paper.tex
last changes and addition of 2 evaluation tables

\documentclass[a4paper]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{fancyhdr}
\usepackage{vmargin}
\usepackage{multirow}	
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{comment}
\usepackage{url}
\usepackage{graphics}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{color}
\usepackage{framed}
\usepackage{hyperref}
\usepackage{epsfig}
\usepackage{tikz}
\usepackage{float}
\usepackage{subcaption}
\usepackage{forest,calc}
\usepackage{tikz-qtree}
\usepackage{color}
\usepackage{colortbl}
\usepackage{capt-of}

\setlength{\parindent}{0pt}
\setlength{\parskip}{5pt}
\setlength{\headheight}{24pt}
\setlength{\headsep}{24pt}

@@

\rhead{\begin{tabular}{rc} 
		\StudNameOne\\
		\StudNameTwo\\
		\StudNameThree\\
		\StudNameFour\\
\end{tabular}}

\author{\StudNumeOne}

\newcommand{\subtitle}{\textbf{Singing Voice Synthesis with DiffSinger}}
\newcommand{\StudNameOne}{\textbf{David Matkovic} - 7038335 }
\newcommand{\StudNameTwo}{\textbf{Jona Hoppe} - 7034173}
\newcommand{\StudNameThree}{\textbf{Hanna Helbig} - 7008726}
\newcommand{\StudNameFour}{\textbf{Maximilian Schmidt} - 2356}

@@

	%==============================================
	%================ Introduction =================
	%==============================================
	\section*{Introduction}

@@

@@

	\color{red}table of mos results\color{black}

	All results are averaged across the models and summarized in \color{red}table 1\color{black}. As expected none of the models surpasses the ground truth value of the vocal separated segments. Additionally the distance between the highest and lowest performing model is with 0.22 score points difference only marginal.

@@

	\color{red}table of results histogram comparison\color{black}

	We implemented all metrics quoted above and tested them on the entirety of our models, using the same test set as for the MOS prediction. Each model is compared with the vocal separated data as our gold standard. The obtained results are averaged for each model and summarized in \color{red}table 2\color{black}.

@@

 	Mixing & Mastering

@@

	\bibliographystyle{plain}  % This style sorts references alphabetically
	\bibliography{references}  % This will load your references.bib file

>>>>

\documentclass[a4paper]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{fancyhdr}
\usepackage{vmargin}
\usepackage{multirow}	
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{comment}
\usepackage{url}
\usepackage{graphics}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{color}
\usepackage{framed}
\usepackage{hyperref}
\usepackage{epsfig}
\usepackage{tikz}
\usepackage{float}
\usepackage{subcaption}
\usepackage{forest,calc}
\usepackage{tikz-qtree}
\usepackage{color}
\usepackage{colortbl}
\usepackage{capt-of}
\usepackage{booktabs}

\setlength{\parindent}{0pt}
\setlength{\parskip}{5pt}
\setlength{\headheight}{24pt}
\setlength{\headsep}{1.5cm}
\setlength{\footskip}{0cm}

@@

\rhead{\begin{tabular}{r} 
		\StudNameOne\\
		\StudNameTwo\\
		\StudNameThree\\
		\StudNameFour\\
\end{tabular}}

\newcommand{\subtitle}{\textbf{Singing Voice Synthesis with DiffSinger}}
\newcommand{\StudNameOne}{\textbf{David Matkovic} - 7038335 }
\newcommand{\StudNameTwo}{\textbf{Jona Hoppe} - 7034173}
\newcommand{\StudNameThree}{\textbf{Hanna Helbig} - 7008726}
\newcommand{\StudNameFour}{\textbf{Maximilian Schmidt} - 2560076}

@@

	\tableofcontents
	\newpage

	%==============================================
	%================ Introduction =================
	%==============================================
	\section{Introduction}

@@

	\newpage

@@

	\begin{table}[ht]
		\centering
		\resizebox{\linewidth}{!}{%
		\begin{tabular}{cccccccccc}
			\toprule
			\textbf{Model} & \textbf{gt} & \textbf{small} & \textbf{large} & \textbf{clean} & \textbf{ft + voc} & \textbf{var+voc} & \textbf{man+clean} & \textbf{man+aug} & \textbf{large+aug} \\
			\midrule
			\textbf{MOS} & \textbf{3.00} & 2.74 & 2.83 & 2.76 & 2.77 & \textbf{2.96} & 2.91 & 2.81 & 2.79 \\
			\bottomrule
		\end{tabular}
		}
		\caption{average MOS predictions across different models}
		\label{tab:mos_scores}
	\end{table}

	All results are averaged across the models and summarized in table \ref{tab:mos_scores}. As expected none of the models surpasses the ground truth value of the vocal separated segments. Additionally the distance between the highest and lowest performing model is with 0.22 score points difference only marginal.

@@

	\begin{table}[ht]
		\centering
		\resizebox{\linewidth}{!}{%
			\begin{tabular}{cccccccccc}
				\toprule
				Model & gt & small & large & clean & ft+voc & var+voc & man+clean & man+aug & large+aug \\
				\midrule
				MOS ↑           & \textbf{3.00} & 2.74 & 2.83 & 2.76 & 2.77 & \textbf{2.96} & 2.91 & 2.81 & 2.79 \\
				Correlation ↑   & --   & \textbf{0.94} & 0.94 & 0.92 & 0.93 & \textbf{0.95} & 0.93 & 0.94 & 0.93 \\
				Chi-Square ↓    & --   & \textbf{248394} & \textbf{298899} & 805762 & 649244 & 575705 & 839064 & 578248 & 360068 \\
				Intersection ↑  & --   & 120777 & \textbf{122109} & 118189 & 119622 & \textbf{122664} & 119577 & 121230 & 121170 \\
				Bhattacharyya ↓ & --   & 0.20 & 0.21 & 0.21 & 0.18 & \textbf{0.16} & 0.18 & 0.18 & \textbf{0.17} \\
				\bottomrule
			\end{tabular}
		}
		\caption{averaged scores of the historgram similarity to ground-truth across different models}
		\label{tab:quantitative_eval}
	\end{table}

	We implemented all metrics quoted above and tested them on the entirety of our models, using the same test set as for the MOS prediction. Each model is compared with the vocal separated data as our gold standard. The obtained results are averaged for each model and summarized in table \ref{tab:quantitative_eval}.

@@

@@

	\newpage
	\bibliographystyle{plain}  % This style sorts references alphabetically
	\bibliography{references}  % This will load your references.bib file
